Spin canonical divisors of log stacky curves

### 2015-06-20 stacky_write_up/spin_cring.tex
major code cleaning
* added linebreaks between theorems/props/lemmata and proofs
* broke long lines
* addressed bad boxes and warnings
* added table of contents (temporary)
* added years to bib entries

@@

\section{Introduction}
\todo{Edit this stuff}
This is our project.
Example, O'Dorney's paper \cite{dorney:canonical}.
We consider divisors of the form $D = \sum_{i = 1}^{r} \subhalf{e_i}$.

\subsection{Main Results}
These are our results.
\begin{thm}
\label{thm:g_0_generators_relations}
Let $(\sx,L)$ be a tame log spin curve over a perfect field $k$, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$. Then the canonical ring 
\begin{align*}
	R(\sx,L) = \bigoplus_{d=0}^\infty H^0(\sx,\sco(L)^{\otimes d})
\end{align*}
is generated as a $k$-algebra by elements of degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions. \todo{Include reference to the table with this list of exceptions.}
\end{thm}
\begin{proof}

@@

In this section, we will prove that if $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions. This is proven in Subsection ~\ref{ssec:g_0_conclusion}. The proof is a rather involved induction. In Subsections ~\ref{ssec:g_0_ram_pts}, ~\ref{ssec:g_0_ram_orders} we prove inductive theorems, and in Subsection ~\ref{ssec:g_0_base} we check the base cases of the induction. Finally, in Subsection ~\ref{ssec:g_0_exceptional} we list out the exceptional cases.

@@

\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1,\ldots, x_n]$ is a graded ring, not necessarily generated in degree 1, is equipped with a monomial ordering $\prec.$ Let $\phi:k[x_1,\ldots, x_n] \rightarrow B$ be a map of graded rings with kernel $I,$ such that $I$ is generated by elements $f_1,\ldots, f_j$, where $in_\prec(f_i) = x_ix_j,$ and no term of $f_i$ is of the form $x_k$. Then, the elements $f_i$ determine minimal generators for $I$.
\end{lem}
\begin{proof}
Regrade the ring $k[x_1,\ldots, x_n]$ so that all $x_i$ lie in degree 1. Then, $\phi:k[x_1,\ldots, x_n]\rightarrow B$ determines a map of rings, no longer necessarily graded. Consider the grlex monomial ordering $<$ on $k[x_1,\ldots, x_n]$. By assumption, the kernel $I$ is generated by elements whose initial terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,\ldots, x_n])_2 = \binom{n}{2}-j.$ This implies any set of generators for $I$ must have at least $j$ elements. Since $f_1,\ldots, f_j$ is such a set, it is minimal.
\end{proof}

\begin{prop}
\label{prop:sat_three_induction}
Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted  log stacky curves $R \subset R'$ be the corresponding inclusion of canonical rings. Let $R_{D'} = R' = k[x]/I'= k[x_3,x_4,x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \frac{1}{3}P$. 
\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3,y_4,y_5]$ with $grlex$ so that $y_3 \prec y_4 \prec y_5$ and equip the ring $k[y_3,y_4,y_5,x]$ with the block order so that $R = k[y_3,y_4,y_5,x]/I$. Let,
	\begin{align*}
	J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
	&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
	&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
\end{align*}
Then, $gin_\prec(I) = J$.
	\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with leading terms as in (b) minimally generate $I$.
\end{enumerate}
\end{prop}
\begin{proof}
First, the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord_P(y_i) = 1$ by Riemann Roch. \todo{Understand why/whether we need to cite lemma 5.4.7.} To complete the proof of (a) we only need show these elements generate $R$ over $R'$. We can first see that the following is a $k$ basis for $R$ over $R'$:
\begin{align}
\label{eqn:add_one_generator}
\begin{split}
	&\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b \geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle \\
	&+\langle y_3^ay_4,y_3^by_5 \mid a \geq 0, b \geq 0 \rangle
\end{split}
\end{align}
To see these generate $R'$ over $R$, note that $\dim R'_d - \dim_k R_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor,$ elements of degree $d$ in the claimed basis of ~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3} \rfloor $ and $b = d \bmod 3$, we have that the elements
\begin{align*}
	x_3^{a-1}x_{3+b},y_3x_3^{a-2}x_{3+b},\ldots, y_3^ax_{3+b},y_3^ay_{3+b}
\end{align*}
are precisely $a$ elements, which are all independent as they have distinct pole orders at $P$. This completes part (a).

To show part (b), note that the generators in ~\ref{eqn:add_one_generator} are precisely a set of monomials which generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it suffices to show that all generators of $J$ lie in $in_\prec(I)$. 
This follows, since there exist constants $A_{i,j} \in k$ for $4 \leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and elements $w_{i,j} \in R'$ so that the following linear combinations of elements lie in $R'$.

\begin{align*}
y_ix_j &- A_{i,j} y_{i-1}w_j & \text{ so that } 4 \leq i \leq 5,3 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
y_4^2 &+ B_1 y_3 y_5 \\
y_4y_5 &+ B_2 y_3^2 x_3 \\
y_5^2 &+ B_3 y_3^2 x_4
\end{align*}
Of course, the initial terms of these elements are precisely the generators of $J$, completing (b).

Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
\end{proof}
\todo{Something is a little fishy with this order, it seems something like: first grade by degree, then try to decrease the highest y, if you cant, try to decrease the highest z, possibly replace $z_5$ by $z_5+Cy_5$ to generic element?}

\ssec{Inductive theorem: Increasing the Ramification Orders}
\label{ssec:g_0_ram_orders}
In this section, we aim to prove the inductive theorem, Theorem ~\ref{thm:ramification_order_induction}. Under fairly general conditions, this theorem will allow us to show that if Theorem ~\ref{thm:ramification_order_induction} holds for a curve with signature $(0;e_1',\ldots, e_r';0)$ then it also holds for a curve with signature $(0;e_1,\ldots, e_r;0)$ with $e_i' - e_i \in \{0,2\}$.

\begin{defn}
\label{defn:admissible}
Let $(\sx',L'),(\sx,L)$ be tame, separably rooted log stacky spin curves, both ramified over ramified at $Q_1,\ldots, Q_r$. Suppose there is a birational map $\sx \rightarrow \sx'$, and let $J \subset \{1,
\ldots, r\}$. Suppose $e_i'+ 2\chi_J(i) = e_i$ where
$$
\chi_J(i) = \begin{cases}
	1, &\text{ if }i \in J\\
	0, &\text{ otherwise. } 
\end{cases}$$
Let $R'$ be the canonical ring associated to $\sx'$. Say $(\sx',J)$, {\bf admissible} if the following three conditions hold.
\begin{enumerate}
	\item[(Ad-i)] Suppose for all $i \in J$, there exists $y_{i,e_i'} \in R'$ so that $R'$ admits a presentation
\begin{align*}
	R' \cong \left( k[x] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
\end{align*}
so that for all $i \in J$ we have $\deg y_{e_i'} = e_i'$ and $-ord_{Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
\item[(Ad-ii)] For all $i \in J$ and $z \neq y_{i,e_i'}$ a generator of $R'$ we have
\begin{align*}
	\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
\end{align*}
\item[(Ad-iii)] For all $i \in J$ we have for all $d \geq 0$,
\begin{align*}
	\deg \lfloor e_i L \rfloor \geq \# S(i,d)
\end{align*}
where
\begin{align*}
	S(i,d) = \{j \in J : j \neq i \text{ and }e_j'+2d \mid e_i+2d\}
\end{align*}
\end{enumerate}
\end{defn}

\begin{lem}
\label{lem:admissible_inequality}
Condition (Ad-ii) of Definition ~\ref{defn:admissible} implies the stronger condition that
\begin{align*}
	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}-\frac{1}{e_i'}
\end{align*}
\end{lem}
\begin{proof}
We know by (Ad-ii) that
\begin{align*}
	-\ord_{Q_i}(z) < \deg(z) \subhalf{e_i'}
\end{align*}
If we write $\frac{\alpha}{\beta} = \deg(z) \frac{e_i'-1}{2e_i'}$ as a fraction in lowest terms, then we see $\beta \mid e_i'$ since $e_i'-1$ is even. Therefore, since $-\ord_{Q_i}(z)$ is an integer, we must have
\begin{align*}
	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}- \frac{1}{\beta} \leq \deg(z) \subhalf{e_i'}- \frac{1}{e_i'}.
\end{align*}
\end{proof}

\begin{thm}
\label{thm:ramification_order_induction}
Suppose $(\sx',L')$ is a tame separably rooted log stacky spin curve is admissible with a generators $y_{i,e_i'} \in R' = R_{L'}$ as in (Ad-i) of Definition ~\ref{defn:admissible}. Then the following are true:
\begin{enumerate}
	\item[(a)] For all $i \in J$, there exists $y_{i,e_i} \in H^0(\sx, e_i(K_\sx))$ so that
	\begin{align*}
	-ord_{Q_i}(y_{i,e_i}) = \frac{e_i-1}{2}
\end{align*}
and
\begin{align*}
	\frac{-\ord_{Q_j}(y_{i,e_i'})}{y_{i,e_i}} \leq \subhalf{e_j'}-\frac{1}{\deg(y_{i,e_i'})e_j'}
\end{align*}
for all $j \in J$ with $j \neq i$.
\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b,$ with $a \geq 0, b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally generate $R$ over $R'$.
\item[(c)] Equip $k[y] = k[y_{i,e_i}]_{i \in J}$ and $k[x]$ with any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with block order. Let $R = k[y,x]/I.$ Then,
\begin{align*}
	in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z \neq y_{i,e_i},y_{i,e_i'} \rangle 
\end{align*}
	as $z$ ranges over all generators of $R$.
	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by products of two monomials and that for all $i \in J$, we have $e_i > \deg z$ for any generator $z$ of $R'.$ Then any set of minimal generators for $I'$ together with any set of relations as in part (c) minimally generate $I$.
	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
\end{enumerate}
\end{thm}
\begin{proof}
Let $(\sx,L)$ and $(\sx',L')$ be the two log stacky spin curves in question, with coarse spaces $X = X'$. Define
\begin{align*}
	S(i,0) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
\end{align*}
Define
\begin{align*}
	E_i = \sum_{j \in S(i,0)}^{}Q_j
\end{align*}
Note that
\begin{align*}
	\lfloor e_i L' \rfloor + Q_i \leq \lfloor e_i L \rfloor 
\end{align*}
and so we obtain an inclusion
\begin{align*}
	H^0(\sx',e_iL'-E_i + Q_j) \rightarrow H^0(\sx,e_iL - E_i) \subset H^0(\sx,e_iL).
\end{align*}
The assumption (Ad-iii) implies
\begin{align*}
	\deg \left( e_i L' - E_i \right) \geq 0
\end{align*}
implying that $H^0(\sx',e_iL'-E_i + Q_i)$ is base point free by Riemann Roch, and so a general element
\begin{align*}
	y_{i,e_i} \in H^0(\sx',e_iL'-E_i + Q_i)
\end{align*}
satisfies
\begin{align*}
	-\ord_{Q_i}(y_{i,e_i}) = \lfloor e_i \subhalf {e_i'} \rfloor +1 = \frac{e_i - 1}{2}
\end{align*}
Therefore, $y_{i,e_i}$ satisfies the first part of the claim of $(a)$.

We next show $y_{i,e_i}$ also satisfies the second part of the claim of $(a),$ by considering seperately the cases of whether $j \in S(i,0),$ and $j \notin S(i,0)$.

If $j \in S(i,0)$ then, since $E_i \geq Q_j$, and $y_{i,e_i} \in H^0(\sx',e_iL'-E_i + Q_i)$,
\begin{align*}
	-\ord_{Q_j}(y_{i,e_i}) \leq e_i\subhalf {e_j'} - 1 \leq e_i \subhalf{e_j'} - \frac{1}{e_j'}.
\end{align*}

If instead $j \notin S(i,0)$, then since $e_j' \nmid e_i$, we know $e_i\subhalf{e_j'} \notin \BZ$, so
\begin{align*}
	-\ord_{Q_j}(y_{i,e_i}) \leq \lfloor  e_i\subhalf{e_j'} \rfloor \leq e_i\subhalf{e_j'} - \frac{1}{e_j'},
\end{align*}
completing the proof of (a).

Next, define $R_0 = R'$ and inductively define 
$$
R_i = \begin{cases}
	R_{i-1} &\text{ if }i \notin J\\
	R_{i-1}[y_{i,e_i}] &\text{ otherwise.} 
\end{cases}$$
To prove (b), it suffices to show that elements of the form $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0, b > 0$ are linearly indpendent, and that these elements together with $R_{i-1}$ span $R_i$ as a $k$-vector space. These elements do not lie in $R_{i-1}$ because their order of pole at $Q_i$ is bigger than the order of any element in $R_{i-1}$, and are linearly independent amongst themselves because of injectivity of the linear map
\begin{align*}
	(a,b) \mapsto \left( \deg\left(y_{i,e_i'}^ay_{i,e_i}^b\right),-\ord_{Q_i}\left( y_{i,e_i'}^ay_{i,e_i}^b \right)  \right) = (a,b) \begin{pmatrix}
	e_i-2 & \frac{e_i-3}{2} \\
	e_i	 & \frac{e_i-1}{2}
\end{pmatrix} 
\end{align*}
The fact the the elements $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0, b > 0$ span $R_i$ over $R{i-1}$ follows from the fact that the integer lattice points in the cone generated by the vectors $\left(e_i-2, \frac{e_i-3}{2} \right)$ and $\left(e_i, \frac{e_i-1}{2} \right)$ is saturated, as the corresponding determinant is
\begin{align*}
	(e_i-2) \frac{e_i-1}{2} - e_i \frac{e_i-3}{2} = 1,
\end{align*}
completing part (b).

To show (c), we wish to show $y_{i,e_i}z \in R'$ for $z \neq y_{i,e_i},y_{i,e_i'}$. Note that $f\in R$ lies in $R'$ if and only if for all $j \in J$ we have
\begin{align*}
	-\ord_{Q_j}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
\end{align*}
We now check this in three cases, depending on whether $j \notin \{i \} \cup S(i,0),j = i,$ or $j \in S(i,0)$.

@@

Here, $-\ord_{Q_j}(L) = -\ord_{Q_j}(L'),$ so
\begin{align*}
	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) \leq e_i \subhalf {e_j'}+ \deg z \subhalf {e_j'} = \deg (y_{i,e_i}z) \subhalf{e_j'}. 
\end{align*}

>>>>

%%%%%%%%%%%%%%%%%%%%% cring custom commands %%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Introduction}
\todo{Edit this stuff}
This is our project.
Example, stuff from Voight and Zureick-Brown \cite{vzb:stacky}
and O'Dorney's paper \cite{dorney:canonical}.
We consider divisors of the form $D = \sum_{i = 1}^{r} \subhalf{e_i}$.

\subsection{Main Results}
These are our results.
\begin{thm}
\label{thm:g_0_generators_relations}
Let $(\sx,L)$ be a tame log spin curve over a perfect field $k$, so
that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$. Then the
canonical ring

\begin{align*}
	R(\sx,L) = \bigoplus_{d=0}^\infty H^0(\sx,\sco(L)^{\otimes d})
\end{align*}

\noindent
is generated as a $k$-algebra by elements of degree at most $e = 
\max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so 
long as $\sigma$ does not lie in a finite list of exceptions. \todo{
Include reference to the table with this list of exceptions.}
\end{thm}
\begin{proof}

@@

In this section, we will prove that if $(\sx , L)$ is a spin curve,
so that $\sx$ has signature $\sigma = (0; e_1, \ldots , e_r; 0)$, then
$R(\sx , L)$ is generated in degree at most $e := \max(5, e_1, \ldots,
e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does
not lie in a finite list of exceptions. This is proven in
Subsection ~\ref{ssec:g_0_conclusion}. The proof is a rather
involved induction. In Subsections ~\ref{ssec:g_0_ram_pts},
~\ref{ssec:g_0_ram_orders} we prove inductive theorems, and in
Subsection ~\ref{ssec:g_0_base} we check the base cases of the
induction. Finally, in Subsection ~\ref{ssec:g_0_exceptional} we
list out the exceptional cases.

@@

\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1,\ldots, x_n]$ is a graded ring, not necessarily
generated in degree 1, is equipped with a monomial ordering $\prec$.
 Let $\phi:k[x_1,\ldots, x_n] \rightarrow B$ be a map of graded
rings with kernel $I,$ such that $I$ is generated by elements $f_1,
\ldots, f_j$, where $in_\prec(f_i) = x_ix_j,$ and no term of $f_i$
is of the form $x_k$. Then, the elements $f_i$ determine minimal
generators for $I$.
\end{lem}

\begin{proof}
Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
degree 1. Then,
\[
	\phi : k[x_1, \ldots, x_n] \rightarrow B
\]

\noindent
determines a map of rings, no longer necessarily graded. Consider
the grlex monomial ordering $<$ on $k[x_1,\ldots, x_n]$. By
assumption, the kernel $I$ is generated by elements whose initial
terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
\ldots, x_n])_2 = \binom{n}{2}-j.$ This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}

\begin{prop}
\label{prop:sat_three_induction}
Let $\sx \rightarrow \sx'$ be a birational map of tame, separably
rooted  log stacky curves $R \subset R'$ be the corresponding
inclusion of canonical rings. Let $R_{D'} = R' = k[x]/I'= k[x_3,x_4
,x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \frac{1}{
3}P$.

\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3,y_4,y_5]$ with $grlex$ so that $y_3 \prec 
		y_4 \prec y_5$ and equip the ring $k[y_3,y_4,y_5,x]$ with the block 
		order so that $R = k[y_3,y_4,y_5,x]/I$. Let,
		\begin{align*}
			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
		\end{align*}
			Then, $gin_\prec(I) = J$.
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{prop}

\begin{proof}
First, the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord
_P(y_i) = 1$ by Riemann Roch. \todo{Understand why/whether we need 
to cite lemma 5.4.7.} To complete the proof of (a) we only need 
show these elements generate $R$ over $R'$. We can first see that 
the following is a $k$ basis for $R$ over $R'$:

\begin{align}
\label{eqn:add_one_generator}
	\begin{split}
		&\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b 
		\geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle \\
		&+\langle y_3^ay_4,y_3^by_5 \mid a \geq 0, b \geq 0 \rangle
	\end{split}
\end{align}

\noindent
To see these generate $R'$ over $R$, note that $\dim R'_d - \dim_k R
_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
,$ elements of degree $d$ in the claimed basis of
~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
\rfloor $ and $b = d \bmod 3$, we have that the elements

\begin{align*}
	x_3^{a-1}x_{3+b},y_3x_3^{a-2}x_{3+b},\ldots, y_3^ax_{3+b},y_3^ay_{
3+b}
\end{align*}

\noindent
are precisely $a$ elements, which are all independent as they have
distinct pole orders at $P$. This completes part (a).

To show part (b), note that the generators in
~\ref{eqn:add_one_generator} are precisely a set of monomials which
generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
suffices to show that all generators of $J$ lie in $in_\prec(I)$.

This follows, since there exist constants $A_{i,j} \in k$ for $4
\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
elements $w_{i,j} \in R'$ so that the following linear combinations
of elements lie in $R'$.

\begin{align*}
	y_ix_j &- A_{i,j} y_{i-1}w_j & \text{ so that } 4 \leq i \leq 5,3
	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
	y_4^2 &+ B_1 y_3 y_5 \\
	y_4y_5 &+ B_2 y_3^2 x_3 \\
	y_5^2 &+ B_3 y_3^2 x_4
\end{align*}

\noindent
Of course, the initial terms of these elements are precisely the
generators of $J$, completing (b).

Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
\end{proof}

\todo{Something is a little fishy with this order, it seems
something like: first grade by degree, then try to decrease the
highest y, if you cant, try to decrease the highest z, possibly
replace $z_5$ by $z_5+Cy_5$ to generic element?}

\ssec{Inductive theorem: Increasing the Ramification Orders}
\label{ssec:g_0_ram_orders}
In this section, we aim to prove the inductive theorem, Theorem
~\ref{thm:ramification_order_induction}. Under fairly general
conditions, this theorem will allow us to show that if Theorem ~\ref
{thm:ramification_order_induction} holds for a curve with signature
$(0;e_1',\ldots, e_r';0)$ then it also holds for a curve with
signature $(0;e_1,\ldots, e_r;0)$ with $e_i' - e_i \in \{0,2\}$.

\begin{defn}
\label{defn:admissible}
Let $(\sx',L'),(\sx,L)$ be tame, separably rooted log stacky spin
curves, both ramified over ramified at $Q_1,\ldots, Q_r$. Suppose
there is a birational map $\sx \rightarrow \sx'$, and let $J \subset
\{1, \ldots, r\}$. Suppose $e_i'+ 2\chi_J(i) = e_i$ where

$$\chi_J(i) = \begin{cases}
	1, &\text{ if }i \in J\\
	0, &\text{ otherwise. } 
\end{cases}$$

Let $R'$ be the canonical ring associated to $\sx'$. Say $(\sx',J)$,
{\bf admissible} if the following three conditions hold.

\begin{enumerate}
	\item[(Ad-i)] Suppose for all $i \in J$, there exists $y_{i,e_i'} 
		\in R'$ so that $R'$ admits a presentation
		\begin{align*}
			R' \cong \left( k[x] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
		\end{align*}
		so that for all $i \in J$ we have $\deg y_{e_i'} = e_i'$ and $-ord_{
		Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
	\item[(Ad-ii)] For all $i \in J$ and $z \neq y_{i,e_i'}$ a 
		generator of $R'$ we have
		\begin{align*}
			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] For all $i \in J$ we have for all $d \geq 0$,
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq \# S(i,d)
		\end{align*}
		where
		\begin{align*}
			S(i,d) = \{j \in J : j \neq i \text{ and }e_j'+2d \mid e_i+2d\}
		\end{align*}
\end{enumerate}
\end{defn}

\begin{lem}
\label{lem:admissible_inequality}
Condition (Ad-ii) of Definition ~\ref{defn:admissible} implies the
stronger condition that

\begin{align*}
	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}-\frac{1}{e_i'}
\end{align*}
\end{lem}

\begin{proof}
We know by (Ad-ii) that

\begin{align*}
	-\ord_{Q_i}(z) < \deg(z) \subhalf{e_i'}
\end{align*}

\noindent
If we write $\frac{\alpha}{\beta} = \deg(z) \frac{e_i'-1}{2e_i'}$ 
as a fraction in lowest terms, then we see $\beta \mid e_i'$ since $
e_i'-1$ is even. Therefore, since $-\ord_{Q_i}(z)$ is an integer, 
we must have

\begin{align*}
	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}- \frac{1}{\beta} \leq 
	\deg(z) \subhalf{e_i'}- \frac{1}{e_i'}.
\end{align*}
\end{proof}

\begin{thm}
\label{thm:ramification_order_induction}
Suppose $(\sx',L')$ is a tame separably rooted log stacky spin
curve is admissible with a generators $y_{i,e_i'} \in R' = R_{L'}$
as in (Ad-i) of Definition ~\ref{defn:admissible}. Then the
following are true:
\begin{enumerate}
	\item[(a)] For all $i \in J$, there exists $y_{i,e_i} \in
		H^0(\sx, e_i(K_\sx))$ so that
		\begin{align*}
			-ord_{Q_i}(y_{i,e_i}) = \frac{e_i-1}{2}
		\end{align*}
		and
		\begin{align*}
			\frac{-\ord_{Q_j}(y_{i,e_i'})}{y_{i,e_i}} \leq \subhalf{e_j'}-
			\frac{1}{\deg(y_{i,e_i'})e_j'}
		\end{align*}
		for all $j \in J$ with $j \neq i$.
	\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b,$ with $a \geq 0,
		b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally
		generate $R$ over $R'$.
	\item[(c)] Equip $k[y] = k[y_{i,e_i}]_{i \in J}$ and $k[x]$ with
		any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with
		block order. Let $R = k[y,x]/I.$ Then,
		\begin{align*}
			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z \neq
			y_{i,e_i},y_{i,e_i'} \rangle
		\end{align*}
		as $z$ ranges over all generators of $R$.
	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
		products of two monomials and that for all $i \in J$, we have $e_i >
		\deg z$ for any generator $z$ of $R'.$ Then any set of minimal
		generators for $I'$ together with any set of relations as in part (c)
		minimally generate $I$.
	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
\end{enumerate}
\end{thm}

\begin{proof}
Let $(\sx,L)$ and $(\sx',L')$ be the two log stacky spin curves in 
question, with coarse spaces $X = X'$. Define

\begin{align*}
	S(i,0) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
\end{align*}

\noindent
Define
\begin{align*}
	E_i = \sum_{j \in S(i,0)}^{}Q_j
\end{align*}

\noindent
Note that
\begin{align*}
	\lfloor e_i L' \rfloor + Q_i \leq \lfloor e_i L \rfloor 
\end{align*}

\noindent
and so we obtain an inclusion
\begin{align*}
	H^0(\sx',e_iL'-E_i + Q_j) \rightarrow H^0(\sx,e_iL - E_i) \subset 
H^0(\sx,e_iL).
\end{align*}

\noindent
The assumption (Ad-iii) implies
\begin{align*}
	\deg \left( e_i L' - E_i \right) \geq 0
\end{align*}

\noindent
implying that $H^0(\sx',e_iL'-E_i + Q_i)$ is base point free by 
Riemann Roch, and so a general element
\begin{align*}
	y_{i,e_i} \in H^0(\sx',e_iL'-E_i + Q_i)
\end{align*}

\noindent
satisfies
\begin{align*}
	-\ord_{Q_i}(y_{i,e_i}) = \lfloor e_i \subhalf {e_i'} \rfloor +1 =
	\frac{e_i - 1}{2}
\end{align*}

\noindent
Therefore, $y_{i,e_i}$ satisfies the first part of the claim of $(a)$.

We next show $y_{i,e_i}$ also satisfies the second part of the
claim of $(a),$ by considering separately the cases of whether $j
\in S(i,0),$ and $j \notin S(i,0)$.

If $j \in S(i,0)$ then, since $E_i \geq Q_j$, and $y_{i,e_i} \in H^0
(\sx',e_iL'-E_i + Q_i)$,
\begin{align*}
	-\ord_{Q_j}(y_{i,e_i}) \leq e_i\subhalf {e_j'} - 1 \leq e_i 
	\subhalf{e_j'} - \frac{1}{e_j'}.
\end{align*}

If instead $j \notin S(i,0)$, then since $e_j' \nmid e_i$, we know
$e_i\subhalf{e_j'} \notin \BZ$, so
\begin{align*}
	-\ord_{Q_j}(y_{i,e_i}) \leq \lfloor  e_i\subhalf{e_j'} \rfloor 
	\leq e_i\subhalf{e_j'} - \frac{1}{e_j'},
\end{align*}

\noindent
completing the proof of (a).

Next, define $R_0 = R'$ and inductively define 
$$R_i = \begin{cases}
	R_{i-1} &\text{ if }i \notin J\\
	R_{i-1}[y_{i,e_i}] &\text{ otherwise.} 
\end{cases}$$

\noindent
To prove (b), it suffices to show that elements of the form $y_{i,e_
i'}^ay_{i,e_i}^b$ with $a \geq 0, b > 0$ are linearly independent,
and that these elements together with $R_{i-1}$ span $R_i$ as a $k$-
vector space. These elements do not lie in $R_{i-1}$ because their
order of pole at $Q_i$ is bigger than the order of any element in $R
_{i-1}$, and are linearly independent amongst themselves because of
injectivity of the linear map

\begin{align*}
	(a,b) \mapsto \left( \deg\left(y_{i,e_i'}^ay_{i,e_i}^b\right),-
	\ord_{Q_i}\left( y_{i,e_i'}^ay_{i,e_i}^b \right)  \right) = (a,b) 
	\begin{pmatrix}
		e_i-2 & \frac{e_i-3}{2} \\
		e_i	 & \frac{e_i-1}{2}
	\end{pmatrix} 
\end{align*}

\noindent
The fact the the elements $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0,
b > 0$ span $R_i$ over $R{i-1}$ follows from the fact that the
integer lattice points in the cone generated by the vectors $\left(e
_i-2, \frac{e_i-3}{2} \right)$ and $\left(e_i, \frac{e_i-1}{2}
\right)$ is saturated, as the corresponding determinant is
\begin{align*}
	(e_i-2) \frac{e_i-1}{2} - e_i \frac{e_i-3}{2} = 1,
\end{align*}
completing part (b).

To show (c), we wish to show $y_{i,e_i}z \in R'$ for $z \neq y_{i,e_
i},y_{i,e_i'}$. Note that $f\in R$ lies in $R'$ if and only if for
all $j \in J$ we have
\begin{align*}
	-\ord_{Q_j}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
\end{align*}

\noindent
We now check this in three cases, depending on whether $j \notin \{
i \} \cup S(i,0),j = i,$ or $j \in S(i,0)$.

@@

Here, $-\ord_{Q_j}(L) = -\ord_{Q_j}(L'),$ so
\begin{align*}
	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) \leq e_i \subhalf {e_j'} +
	\deg z \subhalf {e_j'} = \deg (y_{i,e_i}z) \subhalf{e_j'}. 
\end{align*}
